CRUSE to Safe Cycling in Ireland

### 2023-10-06 paper.qmd
A couple of tweaks (#20)
* A couple of tweaks

* Uptake of cycling

* Be concise

The main aim of the paper is to present the CRUSE Tool and describe the methods and datasets on which the estimates of current and future potential cycling levels are based.
We will also highlight key results, discuss the implications for policy and practice, and outline how similar tools could be developed in other countries.
It is structured as follows.
In @sec-methods, we outline the methods used to generate the evidence presented in the CRUSE Tool for Ireland.
In @sec-results, we present the results of the CRUSE Tool, including estimates of current cycling levels and future cycling potential at the national, regional and local levels.
In @sec-discussion, we discuss the implications of the results for policy and practice.
In @sec-conclusions, we conclude the paper.

>>>>

This paper aims to describe the design, features and potential use of the CRUSE Tool.
In @sec-methods, we outline the methods used to generate the evidence presented in the CRUSE Tool for Ireland.
In @sec-results, we present the results of the CRUSE Tool, including estimates of current cycling levels and future cycling potential at the national, regional and local levels.
In @sec-discussion, we discuss the implications of the results for policy and practice.
In @sec-conclusions, we conclude the paper.
